Thermodynamic fragments in magic state theories

### 2020-11-30 appendix.tex
LC stuff

As a basic example, consider the process 
\begin{equation}
\rho_{\rm{S}}(\epsilon)\too{4} \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(\epsilon')\too{2} \otimes \left( \frac{1}{3}\id \right)\too{2}.
\end{equation}
We want to check which Lorenz curve is higher at the first elbows of the target state, i.e. we want to verify or reject the first inequality below:
\begin{equation}
	L_{\II(\ii,\jj)} \geq L'_{\II'(0, 1, 81)}
\end{equation}
where the first multiplicity of the target state is $m_0 = 1$.
The multiplicities of the initial state are $(1, 384, 4096)$.

@@

In particular, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
\begin{align}
L\left(x_{i'(0, \mlt'_{0}, 9^{\mm})}\right) &\geq L\left(x_{i'(0, m'_{0}, 9^{\mm})}\right), \nonumber\\
L\left(x_{i'(1, \mlt'_{1}, 9^{\mm})}\right) &\geq L\left(x_{i'(1, m'_{1}, 9^{\mm})}\right), \nonumber\\
&\vdotswithin{=} \nonumber\\
L\left(x_{i'(\tt, \mlt'_{r}, 9^{\mm})}\right) &\geq L\left(x_{i'(\tt, m'_{\tt}, 9^{\mm})}\right), \nonumber
\end{align}
where $x_{i'(0, \mlt'_{0}, 9^{\mm'})}, x_{i'(1, \mlt'_{1}, 9^{\mm'})}, \dots, x_{i'(\tt, \mlt'_{\tt}, 9^{\mm'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{\tt}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

>>>>

According to~\cref{thm:elbows} which is proved in~\cref{app:lc_constraints}, for standard Lorenz curves, we need to match indices at the target state elbows, so the requirement on the indices is finding a tuple $(\ii, \jj)$, such that for a given $\ii' = 0,\dots,\tt$,
\begin{equation}
	\jj + \sum_{\dummy=0}^{\ii-1} \mlt_{\dummy}(\nn, \epsilon) = \sum_{\dummy=0}^{\ii'} \mlt_{\dummy}(\tt, \epsilon').
\end{equation}

As a basic example, consider the process 
\begin{equation}
\rho_{\rm{S}}(\epsilon)\too{4} \xrightarrow{\mathcal{O}_{\id/3}} \rho_{\rm{S}}(\epsilon')\too{2} \otimes \left( \frac{1}{3}\id \right)\too{2}.
\end{equation}
We want to check which Lorenz curve is higher at the first elbows of the target state, i.e. we want to verify or reject the first inequality below:
\begin{equation}
	L_{\II(\ii,\jj)} \geq L'_{\II'(0, 1, 81)}
\end{equation}
where the first multiplicity of the target state is $m_0 = 1$.
The multiplicities of the initial state are $(1, 384, 4096)$.

@@

In particular, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
\begin{align}
L\left(x_{\II'(0, \mlt'_{0}, 9^{\mm})}\right) &\geq L\left(x_{\II'(0, m'_{0}, 9^{\mm})}\right), \nonumber\\
L\left(x_{\II'(1, \mlt'_{1}, 9^{\mm})}\right) &\geq L\left(x_{\II'(1, m'_{1}, 9^{\mm})}\right), \nonumber\\
&\vdotswithin{=} \nonumber\\
L\left(x_{\II'(\tt, \mlt'_{r}, 9^{\mm})}\right) &\geq L\left(x_{\II'(\tt, m'_{\tt}, 9^{\mm})}\right), \nonumber
\end{align}
where $x_{\II'(0, \mlt'_{0}, 9^{\mm'})}, x_{\II'(1, \mlt'_{1}, 9^{\mm'})}, \dots, x_{\II'(\tt, \mlt'_{\tt}, 9^{\mm'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{\tt}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

### 2020-11-30 magic_paper.tex
LC stuff

Here we focus on the part of the process described by the LHS of the Lorenz curves, in low noise regimes ($0 \leq \epsilon < 3/7$) with even numbers of initial and target copies.
In this case, the elbow expressions of the standard Lorenz curve in~\cref{eq:lcsu} are given by
\begin{align}
	x_i &= \Phi_+\left(2\ii;\NN,\frac{8}{9}\right), \\
	L_i &= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right),
\end{align}
for $i=0,\dots,\frac{\NN}{2}$, where
\begin{equation}
	\Phi_+(\mmf; \nnf, p) \coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}.
\end{equation}
Conventionally, we set $(x_{-1}, L_{-1}) = (0,0)$.

The coordinates of any point on the Lorenz curve LHS can be expressed as convex sums of the neighbouring elbows,
\begin{align}
    x_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk}\right) x_{\ii-1} + p_{\ii\jj\kk} x_{\ii} \label{eq:lcsu_xcoord}\\
    L_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}
\end{align}
where we use a three-index parametrisation for the coordinates, with $\ii$ determined by the count of the elbow that follows, $\jj$ by the number of Strange state copies and $\kk$ by the number of tensored maximally mixed state copies.
Therefore, for the initial state $\noisysn$ we have
\begin{equation}
	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{\nn}{2\ii}},
\end{equation}
with $\ii=0,\dots,\nn,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\nn}{2\ii}$ and $\kk = 1$.
For the target state $\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}$,
\begin{equation}
	p_{\ii\jj\kk} = \frac{\kk + (\jj-1)9^{\mm}}{9^{\mm} 8^{2\ii}\binom{\tt}{2\ii}}
\end{equation}
with $\ii=0,\dots,\tt,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\tt}{2\ii}$ and $\kk = 1,\dots,9^{\mm}$.

>>>>

Here we focus on the part of the process described by the LHS of the Lorenz curves, in low noise regimes ($0 \leq \epsilon < 3/7$) with even numbers of initial and target copies.
In this case, the elbow expressions of the standard Lorenz curve in~\cref{eq:lcsu} are given by
\begin{align}
	x_i &= \Phi_+\left(2\ii;\NN,\frac{8}{9}\right), \\
	L_i &= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right),
\end{align}
for $i=0,\dots,\frac{\NN}{2}$, where
\begin{equation}
	\Phi_+(2\mmf; \nnf, p) \coloneqq \sum\limits_{\dummy=0}^{\mmf} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}.
\end{equation}
Conventionally, we set $(x_{-1}, L_{-1}) = (0,0)$.

The coordinates of any point on the Lorenz curve LHS can be expressed as convex sums of the neighbouring elbows,
\begin{align}
    x_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk}\right) x_{\ii-1} + p_{\ii\jj\kk} x_{\ii} \label{eq:lcsu_xcoord}\\
    L_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}
\end{align}
where we use a three-index parametrisation for the coordinates, with $\ii$ determined by the count of the elbow that follows, $\jj$ by the number of Strange state copies and $\kk$ by the number of tensored maximally mixed state copies.
Therefore, for the initial state $\noisysn$ we have
\begin{equation}
	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{\nn}{2\ii}},
\end{equation}
with $\ii=0,\dots,\frac{\nn}{2},\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\nn}{2\ii}$ and $\kk = 1$.
For the target state $\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}$,
\begin{equation}
	p_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{\mm}}{9^{\mm} 8^{2\ii'}\binom{\tt}{2\ii'}}
\end{equation}
with $\ii'=0,\dots,\frac{\tt}{2},\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{\tt}{2\ii'}$ and $\kk' = 1,\dots,9^{\mm}$.

Pointwise Lorenz curve comparison requires $x_{\ii\jj\kk} = x_{\ii'\jj'\kk'}$, so we need ot match up the indices appropriately in order to compare $L_{\ii\jj\kk}$ and $L_{\ii'\jj'\kk'}$.
In~\cref{app:lc_compare}, we show that the requirement on the indices is finding a tuple $(\ii, \jj(\ii))$, such that for a given $\ii' = 0,\dots,\frac{\tt}{2}$,
\begin{equation}
	\jj + \sum_{\dummy=0}^{\ii-1} 8^{2\dummy}\binom{\nn}{2\dummy} = \sum_{\dummy=0}^{\ii'} 8^{2\dummy}\binom{\tt}{2\dummy}.
\end{equation}
